Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2017-12-14 paper/paper.Rmd
caption edits

```{r UnusualImages, fig.cap = "Animetrics provided many results that were quite unusual: (a) one of the detected face is a player's back, (b) the KIA logo on the net is detected as a face, (c) is very interesting as the player's face was found, but the shirts of both the player and ball boy were reported as faces, (d) had a lot more faces than many images but Animetrics also found a fist (to the right on the center) that it considered a face. \\label{fig:UnusualImages}", dev="jpeg", dpi=300}
i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(a)")
i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(b)")
i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(c)")
i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(d)")

>>>>

```{r UnusualImages, fig.cap = "Four images in which Animetrics located unusual faces. \\label{fig:UnusualImages}", dev="jpeg", dpi=300}
i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(a)")
i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(b)")
i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(c)")
i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(d)")
